---
title: "COVID-19 In Mexico"
author: "Pragati Prasad"
date: "2024-04-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message=FALSE)
```

```{r}
here::i_am(
  "report.Rmd"
)
```

In this project, we will estimate the effect of chronic conditions (specifically: diabetes, COPD, asthma, immune suppression, CVD, and obesity) on hospitalization and death of COVID-19 patients in Mexico. 

# Descriptive Analysis

## Tabular analysis

Table 1

```{r, table1}
readRDS(
  file = here::here("output/02_table_one.rds")
)
```

Table of Comorbidities

```{r, table2}
readRDS(
  file = here::here("output/02_table2.rds")
)
```
## Graphical Analysis

```{r, plot-data}
#| fig.align = "center",
#| out.width = "600px"
knitr::include_graphics(
  #! TO DO: add appropriate file path to read scatter plot
  here::here("output/02_conditioncount.png")
)
```

```{r}
#| fig.align = "center",
#| out.width = "600px"
knitr::include_graphics(
  #! TO DO: add appropriate file path to read scatter plot
  here::here("output/02_heatmap.png")
)
```

# Statistical Analysis

Effect of chronic conditions (specifically: diabetes, COPD, asthma, immune suppression, CVD, and obesity) on hospitalization of COVID-19 patients in Mexico. 

```{r}
readRDS(
  file = here::here("output/model_1_results.rds")
)
```

```{r}
readRDS(
  file = here::here("output/model_1_effects.rds")
)
```

Effect of chronic conditions (specifically: diabetes, COPD, asthma, immune suppression, CVD, and obesity) on death due to COVID-19 in Mexico. 

```{r}
readRDS(
  file = here::here("output/model_2_results.rds")
)
```

```{r}
readRDS(
  file = here::here("output/model_2_effects.rds")
)
```